\documentclass[letterpaper,10pt]{article}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{datetime}
\usepackage{hang}
\usepackage[stretch=10,shrink=10,protrusion=true]{microtype}
\usepackage{fontspec}

\hyphenpenalty=10000
\tolerance=1000


% Change default font to Ubuntu
\setmainfont{Ubuntu}
% change default font sizes
\renewcommand{\normalsize}{\fontsize{10}{10}\selectfont}

% Formatting section headings
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries}{}{0em}{}

% reduce default spacing between sections
\titlespacing{\section}{0pt}{1.0em}{0.6em}
\titlespacing{\subsection}{0pt}{0.5em}{0.5em}

\newdateformat{monthyear}{\monthname[\THEMONTH] \THEYEAR}

% Remove page numbering
\pagenumbering{gobble}

% Define a new command for job entries with dynamic bullet points
\NewDocumentCommand{\jobentry}{m m m m m m +m}{
    \subsection[#1]{#2\hfill #4}
    \vspace{-0.4em}
    \noindent\textit{#3} \\
    \noindent Technologies: #5 \\
    \vspace{-0.5em}
    \begin{itemize}
        \setlength{\itemsep}{0.4em}
        #6
    \end{itemize}
    \vspace{0.5em}
}

% Reducing space between items in lists
\setlist{nosep}

\begin{document}

\begin{center}
    {\huge\textbf{Josh Fayer}} \\
        \href{https://joshfayer.com}{joshfayer.com} \quad
        \href{mailto:contact@fayer.me}{contact@fayer.me} \quad
        \href{https://linkedin.com/in/joshuafayer}{/in/joshuafayer} \quad (609) 619-1323 \\
        \emph{Updated: \monthyear\today}
\end{center}

\vspace{0.1cm}

\section*{EDUCATION}
\noindent\textbf{Syracuse University, Public Relations, B.S.} \hfill 2016 -- 2020 \\
\emph{Minors: Computer Science, Political Science} \\
GPA: 3.7, \emph{magna cum laude}

\section*{SKILLS}
\noindent\textbf{Languages:} TypeScript, Python, Golang, Shell \\
\noindent\textbf{Full-Stack Development:} Node.js, React.js, Docker, Git \\
\noindent\textbf{Data Pipelines:} SQL, BigQuery, MongoDB, Elasticsearch, TensorFlow, PyTorch, Prompt Engineering \\
\textbf{Cloud Infrastructure:} GCP, Kubernetes, Terraform

\section*{EXPERIENCE}

\jobentry
    {cdns2}
    {Data \& Software Engineer}
    {CleanDNS}
    {04/2024-present}
    {Go, Python, PyTorch, LLMs, TypeScript, Kubernetes, Docker, GCP, SQL, BigQuery, MongoDB}
    {
        \item Developed scalable DNS sinkhole product that handles more than 90 million requests per day.
        \item Overhauled abuse processing pipeline to achieve >85\% accuracy in detecting phishing content.
        \item Built data pipelines and one-off reports in Python, SQL, shell, Elastic, and BigQuery.
        \item Contributed to refactors improve schematization, consistency, performance, and scalability.
    }

\jobentry
    {cdns1}
    {Junior Software Engineer}
    {CleanDNS}
    {10/2023-04/2024}
    {React.js, TypeScript, Node.js, MongoDB, Docker, GCP}
    {
        \item Developed dozens of React components for the CleanDNS frontend.
        \item Developed TypeScript and Python back-end services and integrations with client APIs.
        \item Led effort to improve CI/CD experience through unit testing and deployment automations.
        \item Delivered several automation and analytical concepts to improve efficiency and robustness of the CleanDNS data model, such as algorithms for comparing phishing page HTML structure.
        \item Rearchitected core business ETL pipeline to improve performance and extensibility.
        \item Promoted to Data Engineer in April 2024.
    }

\jobentry
    {bs1}
    {Technology Manager \& Software Engineer}
    {Break Something}
    {10/2021-10/2023}
    {React.js, Node.js, TypeScript, Next.js, SQL, Python, Django, Docker, GCP, Chrome extensions}
    {
        \item Coded and maintained web and cloud applications, including a TypeScript chrome extension, several React-based internal tools, and scalable Python and JavaScript serverless functions.
        \item Managed BI pipeline including building reports in Google Looker Studio, auditing internal data pipeline, and running analyses in SQL.
        \item Built and deployed full-stack product with Python, Django, and MySQL.
        \item Project managed, built and maintained 14 client websites and other front-end web content.
    }

\section*{PROJECTS}

\subsection*{DinoDNS - \href{https://github.com/jafayer/dinodns}{\small{github.com/jafayer/dinodns}}}
\noindent Technologies: TypeScript \\

\begin{itemize}
    \item Designed and built an Express-inspired DNS server framework in TypeScript.
\end{itemize}


% \subsection*{Digital Strategist \hfill 07/2020 -- 10/2021}
% \textit{Break Something | Remote}
% \begin{itemize}
%     \item Wrote, built, and edited hundreds of fundraising and engagement HTML emails for client programs.
%     \item Designed graphics, landing pages, and other creative assets.
%     \item Managed clients' social media presence and conducted social listening.
% \end{itemize}

% \subsection*{Language Transfer - \href{https://github.com/language-transfer}{\small{https://github.com/language-transfer}} \hfill 05/2022 -- 01/2024}
% Technologies: React Native, TypeScript, JavaScript, Xcode, Testflight
% \begin{itemize}
%     \item Served as lead maintainer for iOS version of an open source language learning mobile app.
%     \item Developed new features, issued bug fixes, managed iOS deployment cycle.
% \end{itemize}

% \subsection*{Link Shortener \& CLI \hfill }
% \href{https://fayer.me/short}{fayer.me/short} \\
% Technologies: Golang, JavaScript, AWS Lambda, AWS DynamoDB, AWS API Gateway
% \begin{itemize}
%     \item Built an AWS-based link shortener in JavaScript for my \href{https://fayer.me}{fayer.me} links and a command line interface in Golang to handle CRUD methods and manage the service.
% \end{itemize}

% \subsection*{Nf6.io \hfill }
% \href{https://fayer.me/nf6}{fayer.me/nf6} \\
% Technologies: Node.js, Express, React, SQLite, Cheerio, JavaScript
% \begin{itemize}
%     \item Wrote a full-stack web app to generate customized art based on chess games.
% \end{itemize}

% \subsection*{Election Data Explorer \hfill }
% \href{https://fayer.me/election}{fayer.me/election} \\
% Technologies: Next.js, React, Recharts, JavaScript, API design
% \begin{itemize}
%     \item Built a Next.js site that aggregates and visualizes polling and financial data for every 2022 federal election.
% \end{itemize}

\end{document}